Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-29 writeup/gz_hubble_data.tex
Expand captions on Figures A2-A4. Closes #167.

\subsection{Comparing shallow and full depth morphologies}

@@

\caption{Galaxies whose shallow images were classified as smooth and full depth
images were classified as smooth, intermediate, or featured.}
\label{fig:shallow_smooth}
\end{figure*}

@@

\caption{Galaxies whose shallow images were classified as intermediate and full
depth images were classified as smooth, intermediate, or featured.}
\label{fig:shallow_intermediate}
\end{figure*}

@@

\caption{Galaxies whose shallow images were classified as featured and full
depth images were classified as smooth, intermediate, or featured.}
\label{fig:shallow_featured}
\end{figure*}

>>>>

\subsection{Comparing shallow and full depth morphologies}\label{ssec:depth_comparison}

@@

\caption{Example images of GOODS galaxies that compare GZH morphological
classifications between their 2-epoch and 5-epoch imaging.  The top set (a)
were classified as ``smooth'' in both the 2- and 5-epoch imaging. The
middle set (b) was classified as ``smooth'' in the 2-epoch imaging and as
intermediate between ``smooth'' and ``featured'' in the 5-epoch imaging. The
bottom set (c) was classified as ``smooth'' in the 2-epoch imaging and
``featured'' in the 5-epoch imaging.}
\label{fig:shallow_smooth}
\end{figure*}

@@

\caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
classified as ``intermediate'' in the 2-epoch imaging and ``smooth'' in the
5-epoch imaging. The middle set (b) was classified as intermediate in both the
2- and 5-epoch imaging. The bottom set (c) was classified as ``intermediate''
in the 2-epoch imaging and ``featured'' in the 5-epoch imaging.}
\label{fig:shallow_intermediate}
\end{figure*}

@@

\caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
classified as ``featured'' in the 2-epoch imaging and ``smooth'' in the 5-epoch
imaging (there were only six such images in the sample). The middle set (b) was
classified as ``featured'' in the 2-epoch imaging and ``intermediate'' in the
5-epoch imaging. The bottom set (c) was classified as ``featured'' in both the
2- and 5-epoch imaging.}
\label{fig:shallow_featured}
\end{figure*}
